Replication in Archaeological Science: Shape as a Measure of Weapon Standardisation

### 2020-02-24 analysis/paper.Rmd
adding commentary on subset efforts

ggpairs(total, columns = c("total_length", "blade_length", "socket_length", "sock_bdiam", "sock_sdiam", "width", "thickness"), 
        upper=list(continuous = upper_fn),
        diag=list(continuous = diag_fn),
        lower=list(continuous = "cor")) + theme_minimal() +
        ggsave(here("Images","replication_fig_8_blades_and_sockets.png"))

>>>>

ggpairs(total, columns = c("total_length", "blade_length", "socket_length", "sock_bdiam", "sock_sdiam", "width", "thickness"), 
        upper=list(continuous = upper_fn),
        diag=list(continuous = diag_fn),
        lower=list(continuous = "cor")) + theme_minimal() +
        ggsave(here("Images","replication_fig_8_blades_and_sockets.png"))
```

None of the author-defined data subsets (or a manual calculation based on on complete cases)allows us to replicate the correaltion results.
